---
title: "Group_98_Submission"
author: "MontAlegre, Saygılı, Wen, Tschersich"
date: "18 1 2021"
output: html_document
---
```{r, include = FALSE, message = FALSE, warning = FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggplot2)
library(rgdal)
library(viridis) #for map coloring
library(outliers) #for testing max value in SeoulFloating

#Setting personal working directory with all relevant datasets

if (Sys.info()["user"] == "Rodrigo") {
  setwd("C:/Users/Rodrigo/Desktop/TUM/Wintersemester 2021/Data Analysis and Visualization in R/Case Study/data")
}


#Importing alls .csv files into a list

list_data = list.files(pattern="*.csv")
my_datatables = lapply(list_data, fread)
my_datatables
my_names <- c("case",
              "patientInfo",
              "Policy",
              "Pop_Density",
              "Region",
              "SearchTrend",
              "SeoulFloating",
              "Time",
              "TimeAge",
              "TimeGender",
              "TimeProvince",
              "Weather") #Sorted alphabetically
names(my_datatables) <- my_names

#Mapping list objects to environment

list2env(my_datatables, .GlobalEnv)

```

Our group decided to shift the focus of our case study to take a look at the regional spread of COVID-19, its effect on  Seoul's floating population and patient information.

The first hypothesis is that there is a potential correlation between population density and the number of cases. Since COVID-19 is a virus that spreads due to human interaction in close proximity, it seems plausible that the virus would infect higher amounts of people in regions with a relatively high population density.
```{r, echo = FALSE, message = FALSE}


```

