---
output:
  word_document: default
  df_print: paged
---
---
title: "Group_98_Submission"
author: "MontAlegre, Saygılı, Wen, Tschersich"
date: "23 1 2021"

For our final case study submission, we decided to refocus on answering three hypotheses regarding the correlation between COVID-19 and population density, floating population and the age group of patients.

The first hypothesis is that the amount of confirmed cases is correlated with population density. Intuitively, where there are more people per squre kilometer, there is probably a higher amount of confirmed cases. Two types of plots are presented in order to test this hypothesis. The first depicts the population density of provinces in South Korea, to which the amount of confirmed cases in each province is then added. The data for population density in South Korea is from the Korean Statistical Inforamtion Service. The following code was used to prepare the dataset and create the plot.
```{r setup, echo = FALSE, include = FALSE, message = FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggplot2)
library(rgdal)
library(viridis) #for map coloring
library(outliers) #for testing max value in SeoulFloating
library(ggthemes) # for the theme_map()
library(broom)
library(knitr)

#Setting personal working directory with all relevant datasets

if (Sys.info()["user"] == "Rodrigo") {
  setwd("C:/Users/Rodrigo/Desktop/TUM/Wintersemester 2021/Data Analysis and Visualization in R/Case Study/data")
}

#Importing alls .csv files into a list

list_data = list.files(pattern="*.csv")
my_datatables = lapply(list_data, fread)
my_datatables
my_names <- c("case",
              "patientInfo",
              "Policy",
              "Pop_Density",
              "Region",
              "SearchTrend",
              "SeoulFloating",
              "Time",
              "TimeAge",
              "TimeGender",
              "TimeProvince",
              "Weather") #Sorted alphabetically

names(my_datatables) <- my_names

#Mapping list objects to environment

list2env(my_datatables, .GlobalEnv)

```
```{r, echo = TRUE, include = TRUE, message = FALSE}

pop_dens_col_names <- as.character(Pop_Density[1, ])

names(Pop_Density) <- pop_dens_col_names

Pop_Density[, c("2005", "2010"):= NULL]

Pop_Density <- Pop_Density[2:.N]

Pop_Density[, Pop_dens_sq_km := `2015`][, `2015` := NULL]

infections_by_province <- patientInfo[, .(count = .N), by = c("province",
                                                             "confirmed_date")][, accumulated_sum := cumsum(count)]
infections_by_province[, n_infections := count]

latest_infections <- infections_by_province[order(-as.IDate(confirmed_date, 
                                                             "%Y-%m-%d")), 
                                             head(.SD, 1), 
                                             by = province][, c("count",
                                                                "n_infections") := NULL]
latest_total <- list(province = "Whole country",
                  confirmed_date = as.IDate("2020-06-30"),
                  accumulated_sum = sum(latest_infections$accumulated_sum)) #extra obeservation for country total

latest_infections_national <- rbind(latest_infections, latest_total)

cases_pop_density <- merge(latest_infections, 
                           Pop_Density, 
                           by.x = "province", 
                           by.y = "By administrative divisions", 
                           all = FALSE)


plot_a <- ggplot(cases_pop_density) + #first plot density and cases
  geom_col(aes(x = reorder(province, -accumulated_sum),
               y = accumulated_sum),
           alpha = 0.75,
           width = 0.5,
           fill = "dark blue") +
  labs(title = "Number of Confirmed COVID-19 Cases per Province",
       x = "South Korean Province",
       y = "Number of cases") +
  theme(axis.text.x = element_text(angle = 90),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(size = 12))


plot_cases_popdensity <- plot_a + geom_line(cases_pop_density, 
                                            mapping = aes(x = province,
                                                          y = 0.3*Pop_dens_sq_km,
                                                          group = 1),
                                            color = "dark red", 
                                            size = 3) + 
  scale_y_continuous(limits = c(0, 7000), 
                     breaks = c(0, 1000, 2000, 3000, 4000, 5000, 6000, 7000), 
                     sec.axis = sec_axis(~./0.3, name = "Population Density")) +
  labs(title = "Total confirmed cases versus population density",
       x = "South Korean province",
       y = "Number of cases") +
  theme(plot.title = element_text(size = 12))

```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(plot_a)
```

This first plot depicts the number of confirmed cases in each South Korean province. The provinces with the highest amount of confirmed cases are Jeju-do, Gyeongsangnam-do and Gyeongsangbuk-do. Plotting a line chart that depicts the population density of each province results in the following graph.
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(plot_cases_popdensity)
```

With this new information, it seems that the provices with high amounts of confirmed cases are actually those with lower population density. Another way to depict this visually is to map it onto the South Korean Provinces. The shapefile used to create these maps is from GADM.
```{r, echo = FALSE, message = FALSE, include = FALSE}
korea_map <- readOGR("C:/Users/Rodrigo/Desktop/TUM/Wintersemester 2021/Data Analysis and Visualization in R/Case Study/data/KOR_adm", layer = "KOR_adm1") 

korea_map <- fortify(korea_map, 
                     region = "NAME_1")

cases_pop_density$province <- gsub("Jeju-do", "Jeju", cases_pop_density$province) #changed the name of province Jeju-do to Jeju, since map uses this name

korea_map <- cases_pop_density[korea_map, 
                               on = c("province" = "id")]

map1 <- ggplot(data = korea_map, #this is the base for the maps
               aes(x = long,
                   y = lat,
                   group = group)) + 
  theme(legend.background = element_rect(fill = "white", 
                                         color = "black"))
  
map_cases <- map1 + geom_polygon(aes(fill = accumulated_sum)) +
  labs(title = "Accumulated cases per Province", 
       fill = "Total number of cases") +
  scale_fill_viridis(option = "plasma", 
                     direction = 1) +
  geom_path(aes(x = long, 
                y = lat, 
                group = group), 
            color = "black", 
            size = 1) + 
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3),
        axis.title = element_blank(),
        axis.text = element_blank(),
        plot.background = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.85, 0.25),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.key.size = unit(0.7, "lines")) +
  guides(shape = guide_legend(override.aes = list(size = 1.5)),
         color = guide_legend(override.aes = list(size = 1.5)))

map_pop_density <- map1 + geom_polygon(aes(fill = Pop_dens_sq_km)) +
  labs(title = "Population Density per Province", 
       fill = "Population density") +
  scale_fill_viridis(option = "plasma", 
                     direction = 1) +
  geom_path(aes(x = long, 
                y = lat, 
                group = group), 
            color = "black", 
            size = 1) + 
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3),
        axis.title = element_blank(),
        axis.text = element_blank(),
        plot.background = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.85, 0.25),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 7),
        legend.key.size = unit(0.7, "lines")) +
  guides(shape = guide_legend(override.aes = list(size = 1.5)),
         color = guide_legend(override.aes = list(size = 1.5)))
```
```{r,echo = FALSE}
print(map_cases)
print(map_pop_density)
```

This first visual analysis indicates that populations density and the number of confirmed cases are correlated, albeit negatively. In a second step, we check if the distribution of data is normal or not.

```{r, echo = FALSE}
qqplot1 <- ggplot(data = cases_pop_density, aes(sample = accumulated_sum)) + geom_qq() + stat_qq_line() +
  labs(title = "Q-Q Plot (Confirmed Cases)")

qqplot2 <- ggplot(data = cases_pop_density, aes(sample = Pop_dens_sq_km)) + geom_qq() + stat_qq_line() +
  labs(title = "Q-Q Plot (Population Density)")

print(qqplot1)

print(qqplot2)
```
Since we cannot assume that both variables are normally distributed, we use a spearman's coefficent test to analyze whether the relationship is negatively correlated, to what degree, and if it is statistically significant.
```{r, echo = FALSE}
result1 <- cor.test(cases_pop_density$Pop_dens_sq_km, cases_pop_density$accumulated_sum, method = "spearman")

tidy(result1)
```
Running the spearman's test we get a correlation coefficient of -0.785 and a p-value of 0.0005, meaning that the effect is strong, negative and statistically significant.

The second hypothesis is that the amount of confirmed cases per day in Seoul affected the city's floating population. 
```{r, echo = FALSE, message = FALSE, include = FALSE}
SeoulFloating[, mean_fp_num := mean(fp_num), by = date]


fp_plot <- ggplot(SeoulFloating, aes(x = date,
                                          y = mean_fp_num)) +
  geom_line() +
  labs(title = "Average Floating Population in Seoul over time",
       x = "Date",
       y = "Floating Population Average") +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%B",
               limits = as.Date(c("2020-01-01", "2020-05-31"))) +
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3)) +
  geom_smooth(method = "lm",
              size = 1) +
  scale_y_continuous(breaks = seq(0, 60000, by = 2500))

```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(fp_plot)
```
As shown here, the floating population seems to naturally descrease and increase in periods of time. However, there seems to be a possible outlier occuring in the second half of February. There are also strong decreases in the second half of January, in the first half of March and the beginning of May. Plotting the general trend shows us that it is overall decreasing. Whereas the average floating population was slightly above 27500 in January, this number drops to under 27500 by the end of May.

At the same time, the daily number of confirmed cases also experienced waves. The first seems to have been between March and mid April and the second between mid May to June.
```{r, echo = FALSE, message = FALSE, include = TRUE}
infections_seoul <- patientInfo[province == "Seoul",
                                .(count = .N), 
                                by = c("confirmed_date")][, accumulated_sum := cumsum(count)][confirmed_date <= "2020-05-31"]

dc_plot <- ggplot(infections_seoul,aes(x = confirmed_date,
                                       y = count)) +
  geom_line(size = 1,
            color = "black") + 
  labs(title = "Daily number of confirmed cases in Seoul",
       x = "Date",
       y = "Number of cases per day") +
  theme(panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3))
print(dc_plot)
```
The spikes of daily confirmed cases may be correlated with the drops in the floating population average and may also correlate with the overall negative trend. However, during the same period, the average temperature in Seoul rose. This third variable may also correlate with the average floating population.
```{r, echo = FALSE, message = FALSE, include = FALSE}
weather_seoul_2020 <- Weather[date >= "2020-01-01" & date <= "2020-05-31" & province == "Seoul"][, c("date", "avg_temp")] #preparing weather dataset. Rising average temperature could affect floating population average

avg_temp_2020 <- ggplot(weather_seoul_2020, aes(x = date, y = avg_temp)) +
  geom_line() + 
  labs(title = "Daily Average Temperature in Seoul",
       x = "Date",
       y = "Average Temperature") +
  theme(panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3))
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(avg_temp_2020)
```
We can test if both variables have an effect on the floating population by using multiple regression analysis.

```{r, echo = FALSE, message = FALSE, include = FALSE}



SeoulFloating <- merge(SeoulFloating, 
                       infections_seoul, 
                       by.x = "date", 
                       by.y = "confirmed_date", 
                       all = TRUE
                       )

SeoulFloating <- merge(SeoulFloating, 
                       weather_seoul_2020, 
                       by.x = "date", 
                       by.y = "date", 
                       all = FALSE
                       )

colnames(SeoulFloating)[9] <- "daily_count"


lm1 <- lm(mean_fp_num ~ daily_count, 
          data = SeoulFloating)

lm2 <- lm(mean_fp_num ~ daily_count + avg_temp,
          data = SeoulFloating)

lm1 <- tidy(lm1)

lm2 <- tidy(lm2)
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(lm1)
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(lm2)
```

As shown in the first table, the daily count of cases in Seoul has a negative effect on the average floating population and the effect is statistically significant. Once we perform an analysis including average daily temperature, the effect of the daily count diminishes slightly. Both are statistically significant.


The final hypothesis is that different age groups are affected by different infection durations. We used the patient information dataset to calculate an average duration per age group, which in our case is defined as the release date minus the confirmed date. After cleaning the dataset and disregarding patients of unknown ages, we can plot the following graph.
```{r, echo = FALSE, message = FALSE, include = FALSE}
patientInfo[, age := as.numeric(gsub("s", "", age))][,lengthcovid := (released_date - confirmed_date)]
                               
patientInfo$age <- as.factor(patientInfo$age)

patientInfo_age_factor <- patientInfo[complete.cases(patientInfo[, 3])] #without NAs in age column.

patientInfo_age_factor$age <- recode(patientInfo_age_factor$age, 
                            "0" = "0 - 9", 
                            "10" = "10 - 19", 
                            "20" = "20 - 29", 
                            "30" = "30 - 39", 
                            "40" = "40 - 49", 
                            "50" = "50 - 59", 
                            "60" = "60 - 69", 
                            "70" = "70 - 79", 
                            "80" = "80 - 89", 
                            "90" = "90 - 99", 
                            "100" = "100 - 109")
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
plot_c <- ggplot(patientInfo_age_factor,
                 aes(x = age,
                     y = lengthcovid)) +
  geom_boxplot() +
  labs(title = "Average length of COVID-19 infection by age group",
       x = "Age group",
       y = "Amount of time in days") +
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3),
        panel.background = element_blank())

print(plot_c)
```
A first look at this boxplot indicates that the median between age groups up to "50 - 59" is roughly the same and that this median increases for older age groups. Thus, it seems that patients 60 and over might experience a longer infection duration. The next step is to determine whether our data follows a gaussian distribution and then the appropriate statistical test.

The following qqplots indicate that the distribution of the data is not normal.
```{r, echo = TRUE, message = FALSE, include = TRUE}
patientInfo_age_numeric <- patientInfo[, age := as.numeric(gsub("s", "", age))][,lengthcovid := (released_date - confirmed_date)]

patientInfo_age_numeric$age <- as.numeric(patientInfo_age_numeric$age) #for plotting a histogram

qqplot3 <- ggplot(data = patientInfo_age_numeric, aes(sample = lengthcovid)) + 
  geom_qq() + 
  stat_qq_line() +
  labs(title = "QQ-Plot (duration of infection)")

qqplot4 <- ggplot(data = patientInfo_age_numeric, aes(sample = age)) + 
  geom_qq() + 
  stat_qq_line() +
  labs(title = "QQ-Plot (age)")

print(qqplot3)

print(qqplot4)

```

```{r, echo = FALSE, include = TRUE, message = FALSE}
lm3 <- lm(lengthcovid ~ age, data = patientInfo_age_numeric)

lm3 <- tidy(lm3)

print(lm3)

```
The linear regression model suggests that while the effect of age on the duration of infection is statistically significant, its effect is very small and it does not explain a significant amount of variance in the model (multiple R-squared = 0.0365, adjusted R-squared = 0.036).