---
title: "Group_98_Submission"
author: "MontAlegre, Saygılı, Wen, Tschersich"
date: "18 1 2021"
output: html_document

For our final case study submission, we decided to refocus on answering three hypotheses regarding the correlation between COVID-19 and population density, floating population and the age group of patients.

The first hypothesis is that the amount of confirmed cases is correlated with population density. Intuitively, where there are more people, there is probably a higher amount of confirmed cases. Two types of plots are presented in order to test this hypothesis. The first depicts the population density of provinces in South Korea, which is then reinforced by depicting the amount of confirmed cases in each province.
```{r, echo = FALSE, include = FALSE, message = FALSE}

library(data.table)
library(dplyr)
library(tidyr)
library(magrittr)
library(ggplot2)
library(rgdal)
library(viridis) #for map coloring
library(outliers) #for testing max value in SeoulFloating
library(ggthemes) # for the theme_map()
library(gridExtra)

#Setting personal working directory with all relevant datasets

if (Sys.info()["user"] == "Rodrigo") {
  setwd("C:/Users/Rodrigo/Desktop/TUM/Wintersemester 2021/Data Analysis and Visualization in R/Case Study/data")
}

#Importing alls .csv files into a list

list_data = list.files(pattern="*.csv")
my_datatables = lapply(list_data, fread)
my_datatables
my_names <- c("case",
              "patientInfo",
              "Policy",
              "Pop_Density",
              "Region",
              "SearchTrend",
              "SeoulFloating",
              "Time",
              "TimeAge",
              "TimeGender",
              "TimeProvince",
              "Weather") #Sorted alphabetically

names(my_datatables) <- my_names

#Mapping list objects to environment

list2env(my_datatables, .GlobalEnv)

```
```{r, echo = FALSE, include = FALSE, message = FALSE}

pop_dens_col_names <- as.character(Pop_Density[1, ]) #formatting the data for population density

names(Pop_Density) <- pop_dens_col_names

Pop_Density[, c("2005", "2010"):= NULL]

Pop_Density <- Pop_Density[2:.N]

Pop_Density[, Pop_dens_sq_km := `2015`][, `2015` := NULL]

infections_by_province <- patientInfo[, .(count = .N), by = c("province",
                                                             "confirmed_date")][, accumulated_sum := cumsum(count)]
infections_by_province[, n_infections := count]

latest_infections <- infections_by_province[order(-as.IDate(confirmed_date, 
                                                             "%Y-%m-%d")), 
                                             head(.SD, 1), 
                                             by = province][, c("count",
                                                                "n_infections") := NULL]
latest_total <- list(province = "Whole country",
                  confirmed_date = as.IDate("2020-06-30"),
                  accumulated_sum = sum(latest_infections$accumulated_sum)) #extra obeservation for country total

latest_infections_national <- rbind(latest_infections, latest_total)

cases_pop_density <- merge(latest_infections, 
                           Pop_Density, 
                           by.x = "province", 
                           by.y = "By administrative divisions", 
                           all = FALSE)


plot_a <- ggplot(cases_pop_density) + #first plot density and cases
  geom_col(aes(x = reorder(province, -accumulated_sum),
               y = accumulated_sum),
           alpha = 0.75,
           width = 0.5,
           fill = "dark blue") +
  labs(title = "Number of confirmed COVID-19 cases per province in South Korea",
       x = "South Korean Province",
       y = "Number of cases") +
  theme(axis.text.x = element_text(angle = 90),
        panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())


plot_cases_popdensity <- plot_a + geom_line(cases_pop_density, 
                                            mapping = aes(x = province,
                                                          y = 0.3*Pop_dens_sq_km,
                                                          group = 1),
                                            color = "dark red", 
                                            size = 3) + 
  scale_y_continuous(limits = c(0, 7000), 
                     breaks = c(0, 1000, 2000, 3000, 4000, 5000, 6000, 7000), 
                     sec.axis = sec_axis(~./0.3, name = "Population Density")) +
  labs("Number of confirmed COVID-19 cases and population density per South Korean province",
       x = "South Korean province",
       y = "Number of cases")

```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(plot_a)
```
This first plot depicts the number of confirmed cases in each South Korean province. The provinces with the highest amount of confirmed cases are Jeju-do, Gyeongsangnam-do and Gyeongsangbuk-do. Plotting a line chart that depicts the population density of each province results in the following graph.
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(plot_cases_popdensity)
```
With this new information, it seems that the provices with high amounts of confirmed cases are actually those with lower population density. Another way to depict this visually is to create two chloropleth, each one also depicted the number of confirmed cases per South Korean province and each province's population density. 
```{r}
korea_map <- readOGR("C:/Users/Rodrigo/Desktop/TUM/Wintersemester 2021/Data Analysis and Visualization in R/Case Study/data/KOR_adm", layer = "KOR_adm1") #creating a map to visualize the differences. Change this to where the KOR_adm folder is saved and KOR_adm1 should be the shape file for the provinces

korea_map <- fortify(korea_map, 
                     region = "NAME_1") #shape file is now a dataframe

cases_pop_density$province <- gsub("Jeju-do", "Jeju", cases_pop_density$province) #changed the name of province Jeju-do to Jeju, since map uses this name

korea_map <- cases_pop_density[korea_map, 
                               on = c("province" = "id")]

map1 <- ggplot(data = korea_map, #this is the base for the maps
               aes(x = long,
                   y = lat,
                   group = group)) + 
  theme_bw() + #might just remove this theme
  theme(legend.background = element_rect(fill = "white", 
                                         color = "black"))
  
map_cases <- map1 + geom_polygon(aes(fill = accumulated_sum)) +
  labs(title = "Accumulated cases in South Korean Provinces", 
       fill = "Total number of cases") +
  scale_fill_viridis(option = "plasma", 
                     direction = 1) +
  geom_path(aes(x = long, 
                y = lat, 
                group = group), 
            color = "black", 
            size = 1) + 
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3),
        axis.title = element_blank(),
        axis.text = element_blank(),
        plot.background = element_blank(),
        legend.position = c(.85, .15),
        axis.ticks = element_blank())

map_pop_density <- map1 + geom_polygon(aes(fill = Pop_dens_sq_km)) +
  labs(title = "Population Density in South Korean Provinces", 
       fill = "Population density") +
  scale_fill_viridis(option = "plasma", 
                     direction = 1) +
  geom_path(aes(x = long, 
                y = lat, 
                group = group), 
            color = "black", 
            size = 1) + 
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3),
        axis.title = element_blank(),
        axis.text = element_blank(),
        plot.background = element_blank(),
        legend.position = c(.85, .15),
        axis.ticks = element_blank())
```
```{r,echo = FALSE}
print(grid.arrange(map_cases, map_pop_density, ncol = 2))
```
This first visual analysis indicates that populations density and the number of confirmed cases are correlated, albeit negatively. In a second step, we check if the distribution of data is normal or not.
```{r, echo = FALSE}
qqplot1 <- ggplot(data = cases_pop_density, aes(sample = accumulated_sum)) + geom_qq() + stat_qq_line() +
  labs(title = "QQ-Plot for assessing distribution of cases data")

qqplot2 <- ggplot(data = cases_pop_density, aes(sample = Pop_dens_sq_km)) + geom_qq() + stat_qq_line() +
  labs(title = "QQ-Plot for assessing distribution of population density")

qqplots1and2 <- grid.arrange(qqplot1, qqplot2, ncol = 2)
```
Since we cannot assume that both variables are normally distributed, we use a spearman's coefficent test to analyze whether the relationship is negatively correlated, to what degree, and if it is statistically signifiacant.
```{r, echo = FALSE}
cor.test(cases_pop_density$Pop_dens_sq_km, cases_pop_density$accumulated_sum, method = "spearman")
```
Running the spearman's test we get a correlation coefficient of -0.785 and a p-value of 0.0005, meaning that the effect is strong, negative and statistically significant.

The second hypothesis is that the amount of confirmed cases in Seoul affected the city's floating population. Intuitively, as the amount of confirmed cases rises, the government implements policies and awareness increases through media reporting, we should expect some type of decrease in the amount of people moving throughout the city. The following plot depicts the average floating population in Seoul per day and the overall trend.
```{r, echo = FALSE, message = FALSE, include = FALSE}
SeoulFloating[, mean_fp_num := mean(fp_num), by = date]

fp_plot <- ggplot(SeoulFloating, aes(x = date,
                                          y = mean_fp_num)) +
  geom_line() +
  labs(title = "Average Floating Population in Seoul over time",
       x = "Date",
       y = "Floating Population Average") +
  scale_x_date(date_breaks = "1 month",
               date_labels = "%B",
               limits = as.Date(c("2020-01-01", "2020-05-31"))) +
  theme(panel.border = element_rect(color = "black", 
                                    fill = NA, 
                                    size = 3)) +
  geom_smooth(method = "lm",
              size = 1) +
  scale_y_continuous(breaks = seq(0, 60000, by = 2500))
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(fp_plot)
```
As shown here, the floating population seems to naturally descrease and increase in the short time periods. However, there seems to be a possible outlier occuring in the second half of February. There are also strong decreases in the second half of January, in the first half of March and the beginning of May. Plotting the general trend shows us that there is overall a decreasing trend. Whereas the overall trend was slightly above 27500 in January, this number drops to under 27500 by the end of May.
At the same time, the total number of confirmed COVID-19 cases rose over time, as depicted in the following graph.
```{r, echo = FALSE, message = FALSE, include = TRUE}
infections_seoul <- patientInfo[province == "Seoul",
                                .(count = .N), 
                                by = c("confirmed_date")][, accumulated_sum := cumsum(count)]
is_plot <- ggplot(infections_seoul, aes(x = confirmed_date,
                                        y = accumulated_sum)) +
  geom_line(size = 2,
            color = "black") + 
  labs(title = "Total number of confirmed cases in Seoul",
       x = "Date",
       y = "Accumulated number of cases") +
  theme(panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3))
print(is_plot)
```
The increasing amount of confirmed cases may be correlated with the slight decreasing trend of the floating population. However, during the same period, the average temperature in Seoul rose.
```{r, echo = FALSE, message = FALSE, include = FALSE}
weather_seoul_2020 <- Weather[date >= "2020-01-01" & date <= "2020-05-31" & province == "Seoul"][, c("date", "avg_temp")] #preparing weather dataset. Rising average temperature could affect floating population average

avg_temp_2020 <- ggplot(weather_seoul_2020, aes(x = date, y = avg_temp)) +
  geom_line() + 
  labs(title = "Daily Average Temperature in Seoul",
       x = "Date",
       y = "Average Temperature") +
  theme(panel.border = element_rect(color = "black",
                                    fill = NA,
                                    size = 3))
```
```{r, echo = FALSE, message = FALSE, include = TRUE}
print(avg_temp_2020)
```

